### 2016-09-20 Thesis/DCG_sb-wi-thesis-template/Proteasome/proteasome.tex
proteasome additions final edits after erin

\section{Statement of Attribution}
Initial mutant characterization of \textit{rpt4} mutants was performed by Drs. Kwang-Hee Lee and Richard S. Marshall, postdoctoral fellows in the Vierstra Lab. Additionally, Dr. Lee generated the 2XFLAG-RPT4b transgenic line in the \textit{rpt4b-2} background.  I created the 2XFLAG-RPT4a \textit{rpt4a-1} transgenic lines. I developed the affinity purification via the RP with minor modifications from \citep{book10} by changing the primary buffer to HEPES. All mass-spectrometry sample preparation and data analysis in this chapter was completed by myself.  The actual running of the mass spectrometer was either performed by Dr. Mark Scalf in Dr. Lloyd M. Smith’s lab (Department of Chemistry, University of Wisconsin – Madison), or by Dr. Fionn McLoughlin in the Vierstra lab at Washington University.  I cloned the CP interactors PAP1, PBAC1, PBAC2, PBAC3, and PBAC4, and performed yeast-two-hybrid (Y2H) analysis on these.  While the streaking and yeast transformations were accomplished by myself, Dr. Marshall performed the final spotting of the yeast-two hybrid.  All BiFC data was generated by myself.  The HA-PAP1 transgenic line was created by Dr. Adam Book.  I developed the affinity purification for HA-PAP1 and performed the immunoblot analyses.  Native PAGE was performed by Dr. Marshall. \\

@@

Outside of the core subunits, other proteins are known to associate with the proteasome transiently or sub-stoichiometrically. These proteasome-associated proteins, or PAPs, perform a variety of functions including, substrate processing, ubiquitin recycling, and proteasome assembly. DSK2 and RAD23 contribute to the shuttling of ubiquitylated substrates to the proteasome \citep{farmer10, fatimababy10, lin11}, RPN13 helps bind ubiquitylated targets \citep{schreiner08}, UCH37 and other de-ubiquitylating enzymes (DUBs) \citep{vanderlinden15} help process substrates bound to the RP, and a suite of assembly chaperones assist in the construction of both the CP and RP.  While the route(s) for plant proteasome assembly are largely unknown, a possible model has been established in yeast and mammals (see Figure 1.7, and Figure 1.10). In both systems, the Pba3 chaperone (PAC3 in mammals) interacts with Pba4 (PAC4), forming a Pba(PAC)3/4 heterodimer aiding in early stages of CP assembly by binding the $\alpha$5 subunit, and likely adjacent $\alpha$-subunits  \citep{kunjappu14, yashiroda08}. Similarly, Pba1 (PAC1) interacts with Pba2 (PAC2) to form a Pba(PAC)1/2 heterodimer that aide in assembly of the $\alpha$-ring, and subsequently together with Ump1, helps to form 15S half-barrels consisting of $\alpha$1-7/$\beta$1-6 notably lacking the $\beta$7 subunit \citep{kunjappu14, marques07}. While the Pba(PAC)1/2 heterodimer act throughout assembly and can even bind mature CP \citep{stadtmueller12}, the Pba(PAC)3/4 heterodimer leaves upon incorporation of the $\beta$3 subunit prior to the formation of 15S half-barrels, thus only acting at early stages of assembly \citep{hirano08}. Finally, CP maturation occurs concomitant with autolytic cleavage of $\beta$-subunit propeptide-appendages exposing proteolytic N-terminal threonines and subsequent degradation of Ump1, the first substrate of the CP \citep{ramos98}. In addition to these dedicated CP assembly chaperones, in humans and yeast a different suite of other chaperones also guides assembly of the RP, including Nas2, Nas6, Hsm3, and Rpn14 (see Figure 1.10). These RP assembly chaperones typically bind to the C-terminal domains of specific RPT subunits forming modules (Nas2 with Rpt4 and 5, Nas6 with Rpt3, Hsm3 with Rpt1,2 and Rpn1, and Rpn14 with Rpt6) that, importantly, prevent the assembling RPT ring from forming a pre-mature CP-RP interface \citep{park10}.  In plants, MS/MS analyses of \textit{Arabidopsis} proteasomes identified only one putative CP assembly chaperone, PBAC2 (the nomenclature used here is different from yeast (Pba) and mammals (PAC) as both are standard nomenclature for the $\beta$1 and $\alpha$1 subunits in \textit{Arabidopsis}) \citep{book10}, which is an ortholog to PAC2 based on PSI-BLAST sequence analyses \citep{kusmierczyk11, le07}. Together these data suggest that other plant CP assembly chaperones remain to be identified \citep{book10}.  Additionally, these proteomic analyses failed to identify obvious plant RP assembly orthologs, such as NAS2, NAS6 and HSM3, despite the identification of these orthologs in the \textit{Arabidopsis} genome \citep{book10}. Taken together, the current data suggest that our understanding of plant PAPs in general, and CP and RP assembly chaperones in particular, remains incomplete.

@@

\subsection{Transgenic Plants and Growth Conditions}
The \textit{rpt4a-1},\textit{ rpt4a-3},\textit{ rpt4a-4}, and \textit{rpt4b-1}, \textit{rpt4b-2}, and \textit{rpt4b-3} T(transfer)-DNA insertion mutants in the \textit{Arabidopsis thaliana} Columbia-0 ecotype (Col-0) (SALK\_052372, SALK\_128087C, SALK\_135246, SALK\_108556, SALK\_108557, and SALK\_101982C, respectively) were obtained from the \textit{Arabidopsis} Biological Resource Center (The Ohio State University, Columbus, OH). All mutants were backcrossed three times to the Col-0 parent and then made homozygous by self-fertilization. The \textit{PAG1::PAG1-FLAG pag1-1} germplasm was as previously described \citep{book10}. The \textit{rpt4a} and \textit{rpt4b} alleles were tracked by genomic PCR using the T-DNA-specific left border primer (Lba1) in combination with gene-specific primers (see supplemental Table S1 for all primers used in this study). The exact T-DNA insertion positions were determined by sequencing the T-DNA-specific PCR products using BigDye Terminator Sequencing v3.1 (University of Wisconsin - Madison Biotechnology Center). For RT-PCR, total RNA was extracted from 7-day old liquid grown seedlings of the indicated genotypes using the RNAeasy plant mini kit (Qiagen), and then converted to cDNA using oligo-(dT)$_{20}$ primers and the SuperScript III first-strand synthesis system (Invitrogen) both as according to manufactures instructions.  RT-PCR of the converted cDNA was then performed with primer pairs (P1 – P9).

	Transgenic plants expressing FLAG-tagged variants of \textit{RPT4a} and \textit{RPT4b} were constructed as follows. The genomic region encompassing the full coding sequence of \textit{RPT4a (AT5G43010)}, the 600bp sequence upstream of the ATG start codon, which included the 5$^{\prime}$-untranslated region (UTR), and the 3$^{\prime}$-UTR, was PCR-amplified from Col-0 genomic DNA using primer pair (P10 and P11) and cloned into the pDONR221 (Invitrogen) vector via the Gateway™ BP Clonase™ II reaction (Invitrogen). Codons for tandem FLAG (DYKDDDDK) tags were inserted using two rounds of site directed mutagenesis \citep{edelheit09} with primer pairs P12, P13 and P14, P15. The sequence-confirmed \textit{2xFLAG-RPT4a} clone was recombined into the plant transformation vector pMDC123 (which encodes resistance to the herbicide Basta (glufosinate)) via the Gateway™ LR Clonase™ II reaction (Invitrogen). The genomic region including the full coding sequence of \textit{RPT4b (AT1G45000)} (from start to stop codon, lacking the 3’UTR), plus the 2kb sequence upstream of the ATG start codon (including 5$^{\prime}$ UTR) was PCR-amplified from \textit{A. thaliana} Col-0 genomic DNA using the primer pairs P16, P17 (containing the 2XFLAG tag, \textit{NcoI}, and \textit{SmaI} cleavage sites) and P18, P19 (containing a \textit{PstI} and \textit{NcoI} sites) for the coding sequence and upstream region, respectively. The amplified regions and the recipient pCAMBIA3301 vector were digested with \textit{NcoI}, \textit{SmaI}, and \textit{PstI} (New England Biolabs (NEB)), and ligated together using T4 DNA ligase (NEB). The recombinant plasmid was introduced into the \textit{Escherichia coli} TOP10 strain (Invitrogen), and confirmed as correct by sequencing.

The \textit{PAP1} coding sequence was PCR-amplified from Col-0 cDNA using primer pair P20, P21, and cloned into the pDONR221 vector via the Gateway™ BP Clonase™ II reaction. The \textit{PAP1} coding sequence was then recombined in-frame into the plant transformation vector pMDC99 which harbored a 3x-HA tag upstream of the recombination site (resulting in a 3x-HA tag, followed by a short linker RSSRGVHHMITTTLYTKVEMK, followed by the initiator methionine for PAP1) driven by a \textit{UBQ10} promoter. This was accompanied by a hygromycin B resistance gene. All constructs were transformed into plants by the \textit{Agrobacterium tumefaciens}-mediated floral-dip method with the GV3101 agrobacterium strain \citep{clough98, gelvin03, zhang06}. The construction encoding \textit{RPT4a::FLAG-RPT4a} and \textit{RPT4b::FLAG-RPT4b} were transformed into plants harboring the \textit{rpt4a-1} and \textit{rpt4b-2} insertions, while the construction encoding \textit{UBQ10::HA-PAP1} was transformed into \textit{PAG1-FLAG pag1-1} plants. T1 plants were selected with the relevant plant resistance markers (Basta for both the \textit{RPT4a} pCAMBIA3301 vector and the \textit{RPT4b} pMDC123 vector, and hygromycin for the \textit{PAP1} pMDC99 vector). T2, and T3 plants were generated by self-pollination. T3 progeny analysis of herbicide/antibiotic-resistant segregation was used to identify homozygous T2 plants. Expression of the FLAG-RPT4a/b transgenes was confirmed by SDS-PAGE followed by immunoblot analysis of total cell extracts with either the M2 anti-FLAG antibodies (Sigma Catalogue Number (Cat. No.) F1804) or anti-RPT4 antibodies generated by Kwang-Hee Lee (University of Wisconsin). Total cell extracts were prepared from plants were grown for 7-days on 0.8\% agar plates containing standard plant growth medium (GM medium, containing MS salts, and Gamborg’s B5 vitamins \citep{gamborg68, julio06, murashige62}), and 2\% sucrose). Expression of HA-PAP1 was confirmed by SDS-PAGE of total extracts (prepared as above) followed by immunoblot analysis with anti-HA antibodies (Sigma anti-HA antibody, Cat. No. H6908).

@@

\subsection{SDS-PAGE and Native-PAGE Analysis and Silver Staining}
	SDS-PAGE utilized a Tris-glycine buffering system and was prepared according to the protocol originally established by Laemmli \citep{laemmli70} and were performed as described in \citep{marshall17}. Gels were made using 40\% (w/v) acrylamide/bis-acrylamide solution (29:1, Bio-Rad), SDS-PAGE resolving buffer (375 mM Tris-HCl (pH 8.8) and 0.125\% SDS), SDS-PAGE stacking buffer (125 mM Tris-HCl (pH 6.8) and 0.125\% SDS), 0.1\% ammonium persulphate (APS) and polymerized with N,N,N$^{\prime}$,N$^{\prime}$-tetramethylethylenediamine (TEMED) with a final acrylamide concentration of 11\% and 3.5\% for the resolving and stacking gels, respectively. The gels were cast using a Hoeffer Gel casting system into 18 x 16 cm glass plates using 0.75 mm spacers. Proteins were separated with a Hoeffer SE600 electrophoresis unit using Tris-glycine SDS running buffer (25 mM Tris (pH 8.3), 192 mM glycine, 0.1\% SDS; Bio-Rad) at a constant current of 15 mA for 6 hours. Approximately 32 $\mu$L out of 250 $\mu$L of each affinity-purified proteasome preparation was loaded for SDS-PAGE with Laemmli sample buffer. 	 
Native-PAGE gels were prepared according to Book \textit{et al}. \citep{book10}, and performed exactly as described in \citep{marshall17}. A discontinuous Native-PAGE system was used. The lower gel contained 4.6\% acrylamide (w/v), 0.12\% Bis (w/v), 2.3\% sucrose (w/v), Tris-Borate-EDTA (TBE) buffer (89 mM Tris-HCl (pH 8.3), 89 mM boric acid, 2 mM EDTA, Bio-Rad), 0.1\% APS, 5 mM MgCl$_{2}$, 1 mM ATP. The upper gel contained 2.5\% acrylamide (w/v), 0.62\% Bis (w/v), 2.3\% sucrose, TBE, 0.1\% APS, 5 mM MgCl$_{2}$, 1mM ATP. Gels were cast and run as described above. Gels were run using a Hoeffer SE600 electrophoresis unit with TBE buffer supplemented with 0.5 mM ATP instead of Tris-glycine SDS running buffer. Approximately 32 $\mu$L of each proteasome affinity purification was supplemented with 5 $\mu$L of 0.03\% (w/v) xylene cyanol to visualize loading. Gels were run at 4°C at 50V for 16 or 32 (extended Native-PAGE) hours. Silver-staining of all gels was accomplished using a MS-safe short silver nitrate staining protocol \citep{chevallet06}.
\subsection{MS/MS Sample Preparation}
	All chemicals for MS/MS analyses were obtained from Sigma-Aldrich, unless otherwise noted. All solvents used were obtained from Thermo-Fisher and were LC/MS grade or J.T Baker® grade unless otherwise noted. For in-solution digests, 200 $\mu$L of eluent from each proteasome affinity purification was dried down in a Speed Vac™ centrifugal evaporator (Savant Instruments, model number SUC100H) until approximately 25 $\mu$L of volume remained, then resuspended in 100 $\mu$L of 8 M urea. The samples were reduced with 10 mM DTT (1 hour RT), alkylated with 40 mM iodoacetamide (1 hour RT in the dark), quenched with 40 mM DTT (10 min RT) and then digested with approximately 1 $\mu$g of trypsin overnight at 37°C. The samples were acidified with 10\% trifluoroacetic acid (TFA) until the pH was ≤ 2, desalted on C18 Bond Elut OMIX Tips (Agilent) as according to manufacturer’s instructions, and eluted in 75\% acetonitrile (ACN), 0.1\% acetic acid. The samples were then dried in a Speed Vac™ centrifugal evaporator and resuspended in 30 $\mu$L of 5\% acetonitrile, 0.1\% formic acid and stored at -80°C until analyzed by MS/MS.

For digestion of samples run on a native-PAGE gel, silver-stained protein bands were cut into 1-mm3 pieces with a clean razorblade, washed with MilliQ (EMD Millipore) water, and destained with a 1:1 solution of freshly prepared 100 mM sodium thiosulfate (Na$_{2}$S$_{2}$O$_{3}$) and 30 mM potassium ferricyanide (K$_{3}$Fe(CN)$_{6}$) until colorless. Silver-ions were then removed from the gel slices by washing twice with MilliQ water. The slices were dehydrated with a 50\% ACN in 25 mM ammonium bicarbonate (NH$_{4}$HCO$_{3}$) solution, then dried in a Speed Vac™. They were rehydrated with a reducing solution (25 mM DTT in 50 mM ammonium bicarbonate) for 20 minutes at 56°C, to cleave disulfide bonds. The gel pieces were then treated with an alkylating solution (55 mM iodoacetamide in 50 mM ammonium bicarbonate) in the dark for 20 minutes at RT to alkylate free cysteines. The alkylating solution was then removed, the gel slices were washed with MilliQ water, dehydrated in 50\% ACN in 25 mM ammonium bicarbonate solution, and then dried in a Speed Vac™. The ProteaseMax (Promega) in-gel digest protocol was then used to aide in digestion and peptide extraction from gel slices \citep{saveliev13}. Samples were then desalted with self-packed C18 stage-tips \citep{rappsilber03} using a spin protocol \citep{yu14} , dried, and resuspended as described above.
\subsection{MS/MS Analyses}
In-solution-digested peptide mixtures were separated using a Dionex U3000 nano-flow ultra-high performance liquid chromatography system (nUHPLC, Thermo Scientific). The peptides were separated using an Acclaim® PepMap™ RSLC C18 column, 2 $\mu$m particle size, 100 Å pore size, 75 $\mu$m x 15 cm (Thermo Scientific) using a 90 minute linear gradient from 5\% ACN to 33\% ACN with 0.1\% formic acid. Electro-spray ionization (ESI) of separated peptides was performed with a NanoSpray Flex ion source and ionized peptides were subsequently analyzed with a Thermo Q-Exactive Plus high-resolution accurate-mass orbitrap MS/MS. A data-dependent acquisition program was run with an MS1 mass range of 380-1500 m/z at 70,000 mass resolution, with an automatic gain control (AGC) target of 1e6 ion intensity. The top 15 peaks were chosen for higher energy collisional dissociation (HCD) fragmentation at 28\% normalized collision energy with a dynamic exclusion set to 10 s. Product MS2 scans were acquired with a 200-2000 m/z mass range at 17,500 mass resolution, with an AGC target of 8e3. All peaks were recorded in profile mode. All raw files associated with these experiments will be deposited in the PRoteomics IDEntification (PRIDE) database.

>>>>

\section{Statement of Attribution}
Initial mutant characterization of \textit{rpt4} mutants was performed by Drs. Kwang-Hee Lee and Richard S. Marshall, postdoctoral fellows in the Vierstra Lab. Additionally, Dr. Lee generated the 2XFLAG-RPT4b transgenic line in the \textit{rpt4b-2} background.  I created the 2XFLAG-RPT4a \textit{rpt4a-1} transgenic lines. I developed the affinity purification via the RP with minor modifications from \citep{book10} by changing the primary buffer to HEPES. All mass-spectrometry sample preparation and data analysis in this chapter was completed by myself.  The actual running of the mass spectrometer was either performed by Dr. Mark Scalf in Dr. Lloyd M. Smith's lab (Department of Chemistry, University of Wisconsin - Madison), or by Dr. Fionn McLoughlin in the Vierstra lab at Washington University.  I cloned the CP interactors PAP1, PBAC1, PBAC2, PBAC3, and PBAC4, and performed yeast-two-hybrid (Y2H) analysis on these.  While the streaking and yeast transformations were accomplished by myself, Dr. Marshall performed the final spotting of the yeast-two hybrid.  All BiFC data was generated by myself.  The HA-PAP1 transgenic line was created by Dr. Adam Book.  I developed the affinity purification for HA-PAP1 and performed the immunoblot analyses.  Native PAGE was performed by Dr. Marshall. \\

@@

Outside of the core subunits, other proteins are known to associate with the proteasome transiently or sub-stoichiometrically. These proteasome-associated proteins, or PAPs, perform a variety of functions including, substrate processing, ubiquitin recycling, and proteasome assembly. DSK2 and RAD23 contribute to the shuttling of ubiquitylated substrates to the proteasome \citep{farmer10, fatimababy10, lin11}, RPN13 helps bind ubiquitylated targets \citep{schreiner08}, UCH37 and other de-ubiquitylating enzymes (DUBs) \citep{vanderlinden15} help process substrates bound to the RP, and a suite of assembly chaperones assist in the construction of both the CP and RP.  While the route(s) for plant proteasome assembly are largely unknown, a possible model has been established in yeast and mammals (see Figure 1.7, and Figure 1.10). In both systems, the Pba3 chaperone (PAC3 in mammals) interacts with Pba4 (PAC4), forming a Pba(PAC)3/4 heterodimer aiding in early stages of CP assembly by binding the $\alpha$5 subunit, and likely adjacent $\alpha$-subunits  \citep{kunjappu14, yashiroda08}. Similarly, Pba1 (PAC1) interacts with Pba2 (PAC2) to form a Pba(PAC)1/2 heterodimer that aide in assembly of the $\alpha$-ring, and subsequently together with Ump1, helps to form 15S half-barrels consisting of $\alpha$1-7/$\beta$1-6 notably lacking the $\beta$7 subunit \citep{kunjappu14, marques07}. While the Pba(PAC)1/2 heterodimer act throughout assembly and can even bind mature CP \citep{stadtmueller12}, the Pba(PAC)3/4 heterodimer leaves upon incorporation of the $\beta$3 subunit prior to the formation of 15S half-barrels, thus only acting at early stages of assembly \citep{hirano08}. Finally, CP maturation occurs concomitant with autolytic cleavage of $\beta$-subunit propeptide-appendages exposing proteolytic N-terminal threonines and subsequent degradation of Ump1, the first substrate of the CP \citep{ramos98}. In addition to these dedicated CP assembly chaperones, in humans and yeast a different suite of other chaperones also guides assembly of the RP, including Nas2, Nas6, Hsm3, and Rpn14 (see Figure 1.10). These RP assembly chaperones typically bind to the C-terminal domains of specific RPT subunits forming modules (Nas2 with Rpt4 and 5; Nas6 with Rpt3; Hsm3 with Rpt1, Rpt2, and Rpn1; and Rpn14 with Rpt6) that, importantly, prevent the assembling RPT ring from forming a pre-mature CP-RP interface \citep{park10}.  In plants, MS/MS analyses of \textit{Arabidopsis} proteasomes identified only one putative CP assembly chaperone, PBAC2 (the nomenclature used here is different from yeast (Pba) and mammals (PAC) as both are standard nomenclature for the $\beta$1 and $\alpha$1 subunits in \textit{Arabidopsis}) \citep{book10}, which is an ortholog to PAC2 based on PSI-BLAST sequence analyses \citep{kusmierczyk11, le07}. Together these data suggest that other plant CP assembly chaperones remain to be identified \citep{book10}.  Additionally, these proteomic analyses failed to identify obvious plant RP assembly orthologs, such as NAS2, NAS6 and HSM3, despite the identification of these orthologs in the \textit{Arabidopsis} genome \citep{book10}. Taken together, the current data suggest that our understanding of plant PAPs in general, and CP and RP assembly chaperones in particular, remains incomplete.

@@

\subsection{Transgenic Plants and Growth Conditions}
The \textit{rpt4a-1},\textit{ rpt4a-3},\textit{ rpt4a-4}, and \textit{rpt4b-1}, \textit{rpt4b-2}, and \textit{rpt4b-3} T(transfer)-DNA insertion mutants in the \textit{Arabidopsis thaliana} Columbia-0 ecotype (Col-0) (SALK\_052372, SALK\_128087C, SALK\_135246, SALK\_108556, SALK\_108557, and SALK\_101982C, respectively) were obtained from the \textit{Arabidopsis} Biological Resource Center (The Ohio State University, Columbus, OH). All mutants were backcrossed three times to the Col-0 parent and then made homozygous by self-fertilization. The \textit{PAG1::PAG1-FLAG pag1-1} germplasm was as previously described \citep{book10}. The \textit{rpt4a} and \textit{rpt4b} alleles were tracked by genomic PCR using the T-DNA-specific left border primer (Lba1) in combination with gene-specific primers (see Table \ref{table:primers} for all primers used in this study). The exact T-DNA insertion positions were determined by sequencing the T-DNA-specific PCR products using BigDye Terminator Sequencing v3.1 (University of Wisconsin - Madison Biotechnology Center). For RT-PCR, total RNA was extracted from 7-day old liquid grown seedlings of the indicated genotypes using the RNAeasy plant mini kit (Qiagen), and then converted to cDNA using oligo-(dT)$_{20}$ primers and the SuperScript III first-strand synthesis system (Invitrogen) both as according to manufactures instructions.  RT-PCR of the converted cDNA was then performed with primer pairs (P1 - P9).

	Transgenic plants expressing FLAG-tagged variants of \textit{RPT4a} and \textit{RPT4b} were constructed as follows. The genomic region encompassing the full coding sequence of \textit{RPT4a (AT5G43010)}, the 600bp sequence upstream of the ATG start codon, which included the 5$^{\prime}$-untranslated region (UTR), and the 3$^{\prime}$-UTR, was PCR-amplified from Col-0 genomic DNA using primer pair (P10 and P11) and cloned into the pDONR221 (Invitrogen) vector via the Gateway™ BP Clonase™ II reaction (Invitrogen). Codons for tandem FLAG (DYKDDDDK) tags were inserted using two rounds of site directed mutagenesis \citep{edelheit09} with primer pairs P12, P13 and P14, P15. The sequence-confirmed \textit{2xFLAG-RPT4a} clone was recombined into the plant transformation vector pMDC123 (which encodes resistance to the herbicide Basta (glufosinate)) via the Gateway™ LR Clonase™ II reaction (Invitrogen). The genomic region including the full coding sequence of \textit{RPT4b (AT1G45000)} (from start to stop codon, lacking the 3'UTR), plus the 2kb sequence upstream of the ATG start codon (including 5$^{\prime}$ UTR) was PCR-amplified from \textit{A. thaliana} Col-0 genomic DNA using the primer pairs P16, P17 (containing the 2XFLAG tag, \textit{NcoI}, and \textit{SmaI} cleavage sites) and P18, P19 (containing a \textit{PstI} and \textit{NcoI} sites) for the coding sequence and upstream region, respectively. The amplified regions and the recipient pCAMBIA3301 vector were digested with \textit{NcoI}, \textit{SmaI}, and \textit{PstI} (New England Biolabs (NEB)), and ligated together using T4 DNA ligase (NEB). The recombinant plasmid was introduced into the \textit{Escherichia coli} TOP10 strain (Invitrogen), and confirmed as correct by sequencing.

The \textit{PAP1} coding sequence was PCR-amplified from Col-0 cDNA using primer pair P20, P21, and cloned into the pDONR221 vector via the Gateway™ BP Clonase™ II reaction. The \textit{PAP1} coding sequence was then recombined in-frame into the plant transformation vector pMDC99 which harbored a 3x-HA tag upstream of the recombination site (resulting in a 3x-HA tag, followed by a short linker RSSRGVHHMITTTLYTKVEMK, followed by the initiator methionine for PAP1) driven by a \textit{UBQ10} promoter. This was accompanied by a hygromycin B resistance gene. All constructs were transformed into plants by the \textit{Agrobacterium tumefaciens}-mediated floral-dip method with the GV3101 agrobacterium strain \citep{clough98, gelvin03, zhang06}. The construction encoding \textit{RPT4a::FLAG-RPT4a} and \textit{RPT4b::FLAG-RPT4b} were transformed into plants harboring the \textit{rpt4a-1} and \textit{rpt4b-2} insertions, while the construction encoding \textit{UBQ10::HA-PAP1} was transformed into \textit{PAG1-FLAG pag1-1} plants. T1 plants were selected with the relevant plant resistance markers (Basta for both the \textit{RPT4a} pCAMBIA3301 vector and the \textit{RPT4b} pMDC123 vector, and hygromycin for the \textit{PAP1} pMDC99 vector). T2, and T3 plants were generated by self-pollination. T3 progeny analysis of herbicide/antibiotic-resistant segregation was used to identify homozygous T2 plants. Expression of the FLAG-RPT4a/b transgenes was confirmed by SDS-PAGE followed by immunoblot analysis of total cell extracts with either the M2 anti-FLAG antibodies (Sigma Catalogue Number (Cat. No.) F1804) or anti-RPT4 antibodies generated by Kwang-Hee Lee (University of Wisconsin - Madison). Total cell extracts were prepared from plants were grown for 7-days on 0.8\% agar plates containing standard plant growth medium (GM medium, containing MS salts, and Gamborg's B5 vitamins \citep{gamborg68, julio06, murashige62}), and 2\% sucrose). Expression of HA-PAP1 was confirmed by SDS-PAGE of total extracts (prepared as above) followed by immunoblot analysis with anti-HA antibodies (Sigma anti-HA antibody, Cat. No. H6908).

@@

\subsection{SDS-PAGE and Native-PAGE Analysis and Silver Staining}
	SDS-PAGE utilized a Tris-glycine buffering system and was prepared according to the protocol originally established by Laemmli \citep{laemmli70} and were performed as described in \citep{marshall17}. Gels were made using 40\% (w/v) acrylamide/bis-acrylamide solution (29:1, Bio-Rad), SDS-PAGE resolving buffer (375 mM Tris-HCl (pH 8.8) and 0.125\% SDS), SDS-PAGE stacking buffer (125 mM Tris-HCl (pH 6.8) and 0.125\% SDS), 0.1\% ammonium persulphate (APS) and polymerized with N,N,N$^{\prime}$,N$^{\prime}$-tetramethylethylenediamine (TEMED) with a final acrylamide concentration of 11\% and 3.5\% for the resolving and stacking gels, respectively. The gels were cast using a Hoeffer Gel casting system into 18 x 16 cm glass plates using 0.75 mm spacers. Proteins were separated with a Hoeffer SE600 electrophoresis unit using Tris-glycine SDS running buffer (25 mM Tris (pH 8.3), 192 mM glycine, 0.1\% SDS; Bio-Rad) at a constant current of 15 mA for 6 hours. Approximately 32 $\mu$L out of 250 $\mu$L of each affinity-purified proteasome preparation was loaded for SDS-PAGE with Laemmli sample buffer. 	 
Native-PAGE gels were prepared according to Book \textit{et al}. \citep{book10}, and performed exactly as described in \citep{marshall17}. A discontinuous Native-PAGE system was used. The lower gel contained 4.6\% acrylamide (w/v), 0.12\% Bis (w/v), 2.3\% sucrose (w/v), Tris-Borate-EDTA (TBE) buffer (89 mM Tris-HCl (pH 8.3), 89 mM boric acid, 2 mM EDTA, Bio-Rad), 0.1\% APS, 5 mM MgCl$_{2}$, 1 mM ATP. The upper gel contained 2.5\% acrylamide (w/v), 0.62\% Bis (w/v), 2.3\% sucrose, TBE, 0.1\% APS, 5 mM MgCl$_{2}$, 1mM ATP. Gels were cast and run as described above. Gels were run using a Hoeffer SE600 electrophoresis unit with TBE buffer supplemented with 0.5 mM ATP instead of Tris-glycine SDS running buffer. Approximately 32 $\mu$L of each proteasome affinity purification was supplemented with 5 $\mu$L of 0.03\% (w/v) xylene cyanol to visualize loading. Gels were run at 4°C at 50V for 16 or 32 (extended Native-PAGE) hours. Silver-staining of all gels was accomplished using a MS-safe short silver nitrate staining protocol \citep{chevallet06}.
\subsection{MS/MS Sample Preparation}
	All chemicals for MS/MS analyses were obtained from Sigma-Aldrich, unless otherwise noted. All solvents used were obtained from Thermo-Fisher and were LC/MS grade or J.T Baker® grade unless otherwise noted. For in-solution digests, 200 $\mu$L of eluent from each proteasome affinity purification was dried down in a Speed Vac™ centrifugal evaporator (Savant Instruments, model number SUC100H) until approximately 25 $\mu$L of volume remained, then resuspended in 100 $\mu$L of 8 M urea. The samples were reduced with 10 mM DTT (1 hour RT), alkylated with 40 mM iodoacetamide (1 hour RT in the dark), quenched with 40 mM DTT (10 min RT) and then digested with approximately 1 $\mu$g of trypsin overnight at 37°C. The samples were acidified with 10\% trifluoroacetic acid (TFA) until the pH was ≤ 2, desalted on C18 Bond Elut OMIX Tips (Agilent) as according to manufacturer's instructions, and eluted in 75\% acetonitrile (ACN), 0.1\% acetic acid. The samples were then dried in a Speed Vac™ centrifugal evaporator and resuspended in 30 $\mu$L of 5\% acetonitrile, 0.1\% formic acid and stored at -80°C until analyzed by MS/MS.

For digestion of samples run on a native-PAGE gel, silver-stained protein bands were cut into 1-mm$^{3}$ pieces with a clean razorblade, washed with MilliQ (EMD Millipore) water, and destained with a 1:1 solution of freshly prepared 100 mM sodium thiosulfate (Na$_{2}$S$_{2}$O$_{3}$) and 30 mM potassium ferricyanide (K$_{3}$Fe(CN)$_{6}$) until colorless. Silver-ions were then removed from the gel slices by washing twice with MilliQ water. The slices were dehydrated with a 50\% ACN in 25 mM ammonium bicarbonate (NH$_{4}$HCO$_{3}$) solution, then dried in a Speed Vac™. They were rehydrated with a reducing solution (25 mM DTT in 50 mM ammonium bicarbonate) for 20 minutes at 56°C, to cleave disulfide bonds. The gel pieces were then treated with an alkylating solution (55 mM iodoacetamide in 50 mM ammonium bicarbonate) in the dark for 20 minutes at RT to alkylate free cysteines. The alkylating solution was then removed, the gel slices were washed with MilliQ water, dehydrated in 50\% ACN in 25 mM ammonium bicarbonate solution, and then dried in a Speed Vac™. The ProteaseMax (Promega) in-gel digest protocol was then used to aide in digestion and peptide extraction from gel slices \citep{saveliev13}. Samples were then desalted with self-packed C18 stage-tips \citep{rappsilber03} using a spin protocol \citep{yu14} , dried, and resuspended as described above.
\subsection{MS/MS Analyses}
In-solution-digested peptide mixtures were separated using a Dionex U3000 nano-flow ultra-high performance liquid chromatography system (nUHPLC, Thermo Scientific). The peptides were separated using an Acclaim® PepMap™ RSLC C18 column, 2 $\mu$m particle size, 100 Å pore size, 75 $\mu$m x 15 cm (Thermo Scientific) using a 90 minute linear gradient from 5\% ACN to 33\% ACN with 0.1\% formic acid. Electro-spray ionization (ESI) of separated peptides was performed with a NanoSpray Flex ion source and ionized peptides were subsequently analyzed with a Thermo Q-Exactive Plus high-resolution, accurate-mass Orbitrap MS/MS. A data-dependent acquisition program was run with an MS1 mass range of 380-1500 \textit{m/z} at 70,000 mass resolution, with an automatic gain control (AGC) target of 1e6 ion intensity. The top 15 peaks were chosen for higher energy collisional dissociation (HCD) fragmentation at 28\% normalized collision energy with a dynamic exclusion set to 10 s. Product MS2 scans were acquired with a 200-2000 \textit{m/z} mass range at 17,500 mass resolution, with an AGC target of 8e3. All peaks were recorded in profile mode. All raw files associated with these experiments will be deposited in the PRoteomics IDEntification (PRIDE) database.

Peptide samples obtained from native-gel slices were instead analyzed using a nUHPLC (nanoAcquity, Waters Corporation) connected online to an electrospray ionization LTQ Velos Orbitrap mass spectrometer (Thermo Scientific).  Separation of the peptide mixture employed a 100 x 365 $\mu$m fused silica capillary micro-column packed with 20 cm of 1.7 $\mu$m-diameter, 130-Å pore size, C18 beads (Waters BEH), with an emitter tip pulled to approximately 1 $\mu$m using a laser puller (Sutter Instruments).  Peptides were separated with a 2\% to 30\% acetonitrile gradient in 0.1\% formic acid.  Full-mass scans were performed in the FT Orbitrap with a mass range of 300-1500 \textit{m/z} at a resolution of 60,000, followed by ten MS/MS high energy C-trap dissociation scans of the ten highest intensity parent ions at 42\% normalized collision energy and 7,500 resolution, with a mass range starting at 100 \textit{m/z}.  Dynamic exclusion was enabled with a repeat count of two over the duration of 30 s and an exclusion window of 120 s.
\subsection{MS/MS Data Processing}
For the proteasome associated protein studies, raw spectra files were processed with MaxQuant version 1.5.3.30 \citep{cox08} using the Andromeda search engine against a TAIR10\_pep\_20101214\_updated.fasta file obtained from The \textit{Arabidopsis} Information Resource (TAIR) version 10 \citep{berardini15}. Andromeda searches were performed with MS1 mass tolerance of 20 ppm and an MS2 mass tolerance of 10 ppm. Up to two missed cleavages were allowed, along with the fixed modifications of carbamidomethyl on cysteine, and variable modifications including oxidation of methionine, acetylation of protein N-termini, and GlyGly (ubiquitylation remnant after cleavage with trypsin) on lysines for possible ubiquitylation events, were specified. Peptides and protein groups were identified with a 0.01 false discovery rate (FDR).
